Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-31 tex/comments/3-nat-comments.tex
Some edits to conjectures section

  \textbf{(ii)}
  Since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
  This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
  if $\lambda = \varsigma$, then we have that \[\beta_\varsigma(1,2) = 4 \equiv 0 \pmod e,\] a contradiction.
  Hence $\lambda = \mu$.
\end{proof}
This will be an integral technical tool in proving the correspondence between the crossingless matchings representation $M_{2n + r}^r$ and the Specht module $S^{(n+r,n)}$ in the following section.

@@

\subsection{Sign subrepresentations when $e\nmid n+r+1$}\,
\label{kernel}

{\color{magenta} \Huge PLEASE ADDRESS: $W$ needs to be replaced with $M$.} 
{\color{magenta} Also, titles should be lower case (I fixed in this document), and can be more descriptive\ldots e.g. ``Sign subrepresentations of the crossingless matching; characterizing the sign subrepresentation; Sign subrepresentations when e = n+r+1.}

@@

We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
It is a classical result that a representation $M$ is irreducible if and only if every nonzero element of $M$ is cyclic \cite{Etingof}.
We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
the following lemma is integral in showing this.

@@

 Due to the argument present in Theorem \ref{Irreducibility Theorem}, sign subrepresentations provide a surprisingly strong characterization of some $M_{2n + r}^r$ as follows.
 \begin{proposition}\label{Preimage of K}
 	{\color{red!80!green}This proposition can be strengthened, right? Like we just need a sequence of $n-n'$ actions such that no two of them are closer than two positions apart, right?}
 	Fix some $M := M_{2n + r}^r$.
 	Suppose there is some natural number $n'$ with $n' \leq n$ such that $K_{2n' + r}^r \neq 0$.
 	Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
 	\[
 	\pi := \begin{cases}
 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n,'\\
 	\id{M} & \text{if } n = n',
 	\end{cases}
 	\]
 	where $\id M$ is the identity map on $M$.
 	Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
 \end{proposition}
 \begin{proof}
 	It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
 	then, any subrepresentation containing $w$ also contains all of $M$, implying the proposition.

@@

 This is suggestive;
 the preimage $\pi^{-1}(K)$ may be integral in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
 The following section poses several conjectures involving this structure.

 \subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
 If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Propostion \ref{Preimage of K}.
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
 the same appears to be true of $M_{2n + r}^r$ by Figures \ref{Composition series e=3} through \ref{Composition series e=6}.
 This motivates our first conjecture:
 \begin{conjecture}\label{Preimage subrepresentation}
 	In Proposition \ref{Preimage of K}, $\pi^{-1}(K)$ is an irreducible subrepresentation of $M$.
 \end{conjecture}
 {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}

 We can posit more sturcutre than this;
 by observing Figure \ref{Empirical Kernel}, we note that the kernel is nontrivial in more cases than $e = n + r + 1$, and appears to follow a pattern: 
 \begin{conjecture}\label{Sharp kernel}
 	Suppose $p = \infty$.
 	Then, $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$ and $e < n$. in which case it is one-dimensional.
 \end{conjecture} 
 Then, assuming that Conjectures \ref{Preimage subrepresentation} and \ref{Sharp kernel} are true, we reach the following corollary.
 \begin{corollary}
 	Suppose $e,n,r$ are such that $M_{2n + r}^r$ is irreducible and $e \mid n' + r + 1$ for some $e < n' < n$.
 	Then, $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
 	0 \subset \pi^{-1}(K) \subset M.\end{equation}
 \end{corollary}
 \begin{proof}
 	By \ref{Sharp kernel}, we have the filtration \eqref{Conjecture filtration}.
 	By \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K}, the second factor is irreducible.
 \end{proof}

 These conjectures hope to characterize much of the structure of $M_{2n + r}^r$.
 Due to this structure, the heuristics listed above, their isomorphism in the $e > n + r + 1$ case, and the equality of their dimension, we pose the following conjecture.
 \begin{conjecture}
 	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 \end{conjecture}

\section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
The irreducibility of $S^{(n+r,n)}$ is integral to arguments of Section \ref{Crossingless Matchings Section};
without irreducibility of $M_{2n + r}^r$ (which is conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
Further, when $S^{(n+r,n)}$ is reducible, we have $e \mid l$ for some $r+2 \leq l \leq n+r+1$, and hence the filtration provided in Proposition \ref{Filtration} fails to be a composition series.
In summary, for $S^{(n+r,n)}$, nearly every argument in Sections \ref{Specht Modules Section} and \ref{Crossingless Matchings Section} break down, and hence it is difficult to characterize the Specht module $S^{(n+r,n)}$ via crossingless matchings.

@@

\begin{figure}[h]
  \[
    \ENRGrid{13/7}{2/1,5/1,8/1,11/1,1/2,4/2,7/2,10/2}
  \]\[
    \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
  \]
  \caption{
    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 3,4$ respectively.
    The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e < n$.
  }\label{Empirical Kernel}
\end{figure}

>>>>

  \textbf{(ii)}
  Since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
  This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
  if $\lambda = \varsigma$, then we have that \[\beta_\varsigma(1,2) = 4 \equiv 0 \pmod e,\] a contradiction.
  Hence $\lambda = \mu$.
\end{proof}
This will be an important technical tool in proving the correspondence between the crossingless matchings representation $M_{2n + r}^r$ and the Specht module $S^{(n+r,n)}$ in the following section.

@@

\subsection{Sign subrepresentations when $e\nmid n+r+1$}
\label{kernel}

@@

We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
It is a classical result that a representation $M$ is irreducible if and only if every nonzero element of $M$ is cyclic \cite{Etingof}.
We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
the following lemma is plays a key role in showing this.

@@

 Due to the argument present in Theorem \ref{Irreducibility Theorem}, sign subrepresentations provide a surprisingly strong characterization of some $M_{2n + r}^r$ as follows.
 \begin{proposition}\label{Preimage of K}
 	{\color{red!80!green}This proposition can be strengthened, right? Like we just need a sequence of $n-n'$ actions such that no two of them are closer than two positions apart, right?}
 	Fix some $M := M_{2n + r}^r$.
 	Suppose there is some natural number $n'$ with $n' \leq n$ such that $K_{2n' + r}^r \neq 0$.
 	Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
 	\[
 	\pi := \begin{cases}
 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n,'\\
 	\id{M} & \text{if } n = n',
 	\end{cases}
 	\]
  where $\id M$ is the identity map on $M_{2n + r}^r$.
  Then, $\pi^{-1}(K_{2n' + r}^r)$ contains any proper subrepresentations of $M_{2n + r}^r$.
 \end{proposition}
 \begin{proof}
 	It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
 	then, any subrepresentation containing $w$ also contains all of $M$, implying the proposition.

@@

 This is suggestive;
 the preimage $\pi^{-1}(K)$ may play a key role in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
 The following section poses several conjectures involving this structure.

 \subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
 If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Proposition \ref{Preimage of K}.
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[Appendix~B]{Mathas-book};
 this is give heuristic support in Appendix \ref{Empirics Section}.
 This motivates our first conjecture:
 \begin{conjecture}\label{Preimage subrepresentation}
   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M$.
 \end{conjecture}
 {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}
 This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
 In general, this is surprising;
 $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.

 We can posit more structure than this;
 by observing Figure \ref{Empirical Kernel}, we note that the kernel is nontrivial in more cases than $e = n + r + 1$, and appears to follow a pattern: 
 \begin{conjecture}\label{Sharp kernel}
 	Suppose $p = \infty$.
  Then, $K_{2n + r}^r \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$ and $e > n$, in which case it is one-dimensional.
 \end{conjecture} 
 Then, assuming that Conjectures \ref{Preimage subrepresentation} and \ref{Sharp kernel} are true, we reach the following corollary.
 \begin{corollary}
  Assume Conjectures \ref{Preimage subrepresentation} and \ref{Sharp kernel}.
 	Suppose $e,n,r$ are such that $M_{2n + r}^r$ is irreducible and $e \mid n' + r + 1$ for some $e < n' < n$.
 	Then, $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
    0 \subset \pi^{-1}(K_{2n' + r}^r) \subset M_{2n + r}^r.\end{equation}
 \end{corollary}
 \begin{proof}
 	By Conjecture \ref{Sharp kernel}, we have the filtration \eqref{Conjecture filtration}.
 	By Conjecture \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K}, the second factor is irreducible.
 \end{proof}

 These conjectures would characterize much of the structure of $M_{2n + r}^r$.
 We will pose a final conjecture as follows.
 \begin{conjecture}
 	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 \end{conjecture}
 The support for this includes {\color{magenta} FILL THIS IN.}

\section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
The irreducibility of $S^{(n+r,n)}$ plays a central role in the arguments of Section \ref{Crossingless Matchings Section};
without irreducibility of $M_{2n + r}^r$ (which is conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
Further, when $S^{(n+r,n)}$ is reducible, we have $e \mid l$ for some $r+2 \leq l \leq n+r+1$, and hence the filtration provided in Proposition \ref{Filtration} fails to be a composition series.
In summary, for $S^{(n+r,n)}$, nearly every argument in Sections \ref{Specht Modules Section} and \ref{Crossingless Matchings Section} break down, and hence it is difficult to characterize the Specht module $S^{(n+r,n)}$ via crossingless matchings.

@@

\begin{figure}[h]
  \[
    \ENRGrid{13/7}{2/1,5/1,8/1,11/1,1/2,4/2,7/2,10/2}
  \]\[
    \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
  \]
  \caption{
    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 3,4$ respectively.
    The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e > n$.
  }\label{Empirical Kernel}
\end{figure}
